### 2023-03-02 supplement/unionFindPTS.tex
Edits supplemental material for type hole inference stuff. Spacing is still a little funky in section B and I'm not quite sure why (Raef)
Updates from Overleaf

\newpage
\section{Appendix A: An implementation of union-findable Possible Type Sets}

@@

\end{lstlisting}
\vspace{-4px}
 \hrule
\caption{An Implementation of \textit{PossibleTypeSet} using UnionFind}
\label{fig:ufalgcode}
\end{figure}

>>>>

\newpage
\section{An implementation of union-findable Possible Type Sets}

@@

\end{lstlisting}
 \hrule
\caption{An Implementation of \textit{PossibleTypeSet} using UnionFind}
\label{fig:ufalgcode}
\end{figure}

\begin{figure}[htb!]
\begin{lstlisting}[escapeinside={(*}{*)}]
let create_traversable_edge (graph, t1, t2) =
    let (rep1, rep2) = (UnionFind.find(t1), UnionFind.find(t2)) in
    let (s1, s2) = (Map.find(graph, rep1), Map.find(graph, rep2)) in
    let union_rep = UnionFind.union(rep1, rep2) in
    let s_merged = s1 (*$\amalg_{UF}$*) s2 in
    Map.update(graph, union_rep, s_merged);;
let create_solution_edge (graph, t1, t2) =
    let rep1 = UnionFind.find(t1) in
    let s = Map.find(graph, rep1) in
    let s' = s (*$\amalg_{UF}$*) UnionFind.elem(single(t2)) in
    Map.update(graph, t1, s');;
\end{lstlisting}
\hrule
\caption{Constraint solving algorithm helper functions, using Union-Find.}
\label{fig:algcode_construct_graph_helpers}
\end{figure}

\begin{figure}[htb!]
\begin{lstlisting}[escapeinside={(*}{*)}]
let handle_occurs_check (graph) =
    let annotate_with_error (key) =
        let s = Map.find(graph, UnionFind.find(key) in
        let pass_occurs = is_acyclic(s)
        (key, s, pass_occurs)
    in
    List.map(Map.keys(graph), annotate_with_error);;
\end{lstlisting}
 \hrule
\caption{Occurs check assessment}
\label{fig:occurs_check}
\end{figure}
